Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2017-06-21 article/article.tex
inserted line numbers

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Are environmental and geographic effective surrogates for genetic variation in conservation planning?},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Are environmental and geographic effective surrogates for genetic
variation in conservation planning?}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Cynthia Riginos$^1$, Hugh
P. Possingham$^1$, Richard A. Fuller$^1$\\$^1$School of Biological
Sciences, The University of Queensland, Brisbane, QLD,
Australia\\$^2$School of Geography, Planning and Environmental
Management, The University of Queensland, Brisbane, QLD,
Australia\\Correspondance should be addressed to
\href{mailto:jeffrey.hanson@uqconnect.edu.au}{jeffrey.hanson@uqconnect.edu.au}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{01 January 2016}

% load packages
\usepackage{amsmath,amsfonts,float,makecell,titletoc,tocloft,titlesec,natbib,pdfpages}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}

% format captions
\usepackage[labelfont={small,bf}, labelsep=space, font={small}]{caption}

% format headings
\titleformat{\subsection}
{\normalfont\Large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
{\normalfont\large\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titleformat{\subparagraph}
{\normalfont\normalsize\itshape}{\thesubparagraph}{1em}{}

\titlespacing\paragraph{0pt}{12pt plus 4pt minus 2pt}{+0pt plus 2pt minus 2pt}
\titlespacing{\subparagraph}{0pt}{6pt plus 4pt minus 2pt}{+0pt plus 2pt minus 2pt}

% format toc
\renewcommand\cftsubsecfont{\normalfont\normalsize\bfseries}
% \renewcommand\cftsubsubsecfont{\normalfont\normalsize\bfseries}
% \renewcommand\cftparafont{\normalfont\normalsize\bfseries}
% \renewcommand\cftsubparafont{\normalfont\normalsize\itshape}

% make figures static
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
	\expandafter\origfigure\expandafter[H]
} {
	\endorigfigure
}

@@

\maketitle

\begin{abstract}
Insert abstract here.
\end{abstract}

\subsection{Introduction}\label{introduction}

\subsection{Methods}\label{methods}

\subsubsection{Study area}\label{study-area}

To address the aims of the study, we utilized species distribution and
genomic data collected by the IntraBioDiv project (Figure S1; Meirmans
\emph{et al.} 2011; see Gugerli \emph{et al.} 2008 for methodological
details). This dataset was well suited for this study, because it
provides spatially explicit genomic data for a multitude of species
across a broad geographic area and over large environmental gradients.
As part of this project, data for 27 alpine plant species were collected
across the European Alps according to a grid (22.3 km $\times$ 25 km).
Briefly, in every second cell, plant samples were collected from three
individuals for each species present inside the cell. Samples were
genotyped using amplified fragment length polymorphisms (AFLP; Vos
\emph{et al.} 1995). Matrices denoting the presence/absence of
polymorphisms at loci were constructed independently for each species.
Thus for each second grid cell, for each of the species in the grid
cell, the dataset contains information describing the genomic variation
of individuals inside the grid cell. We used these grid cells as
planning units to develop prioritizations to investigate the
effectiveness of surrogates for the (AFLP) genetic variation.

\subsubsection{Surrogate data}\label{surrogate-data}

We explored the effectiveness of climatic and geographic surrogates. To
describe variation in the location of each grid cell, we projected the
grid into an equi-distant coordinate system (ESRI:102031) and used the
centroid of each cell. To describe the climatic variation among each
cell, we obtained twenty-one bioclimatic variables (approx. 1km
resolution; Hijmans \emph{et al.} 2005). These layers and the grid cells
were projected into an equal-area coordinate system (ESRI:102014). The
bioclimatic variables were clipped to the extent of the grid and subject
to a principle components analysis (PCA; Table S1). The first two
principle components (PCs) cumulatively explained 97.2\% of the
variation and were used to generate two new layers. We calculated the
average value for each PC layer in each grid cell, and used these values
to characterize the main themes of climatic variation among the grid
cells (Figure S2).

\subsubsection{Outlier locus detection}\label{outlier-locus-detection}

To investigate the effectiveness of the surrogates for adaptive and
neutral genetic variation, we first identified which of the sampled loci
for each species were under selection. We used outlier locus detection
methods (evaluated in P{é}rez-Figueroa \emph{et al.} 2010) to avoid
circularity issues. The basic premise underpinning these analyses is
that neutral loci are expected to have a specific level of variation
among populations ($F_{st}$), and loci that deviate from this
expectation should be under selection. Thus loci can be identified as
being under selection without using environmental data. In an earlier
study, Bothwell \emph{et al.} (2013) applied such outlier detection
methods to one of the species in this dataset (\emph{Getiana nivalis}).
Here, we adopted a similar methodology and applied it to each of the 27
species in the dataset.

First, we grouped individuals into genetic lineages for each species
(Figure S2). The purpose of this step was to avoid confounding variation
between populations with due to genetic history with variation
attributed to selection pressures. We used the Bayesian clustering
method implemented in $\texttt{Structure}$ (version 2.3.4; Pritchard
\emph{et al.} 2000; Falush \emph{et al.} 2007) assuming admixture and an
independent alleles model. For each species, we identified the most
plausible number of populations (K = 1--3; 4 runs per K; 10 burn-in
iterations; 10 post-burn-in iterations) using the $\Delta$K method
(Figure S3; Evanno \emph{et al.} 2005). We aggregated the population
membership probabilities from replicate runs using $\texttt{CLUMPP}$
(version 1.1.2; large K greedy search method with 1000 random starts per
K per species; Figure S4; Jakobsson and Rosenberg 2007). Individuals
with a moderate probability of belonging to a single population
($\geq 0.75$) were assigned accordingly (Figure S5), and subject to
subsequent outlier locus detection methods.

We used $\texttt{Bayescan}$ (version 2.1; Foll and Gaggiotti 2008) to
identify loci under selection for each species (Table S2). For each
species, $\texttt{Bayescan}$ was run using the population memberships
identified in the previous analysis (1:1 prior odds; 3 pilot runs; 40
burn-in iterations; 10 post-burn-in iterations thinned by 1 iterations).
Following guidelines in the $\texttt{Bayescan}$ manual, we omitted loci
where the global frequency of the minor allele was $\geq 0.05$ to avoid
false-positives. To ensure convergence, we ran 2 replicates per species
using a suitable false discovery rate (FDR; $\leq 0.8$; Benjamini and
Hochberg 1995).

After classifying loci as adaptive or neutral, we mapped the main
gradients of the adaptive (if present) and neutral genetic variation for
each species (Figures S4--S29). Note that while individuals not assigned
to populations were omitted from the $\texttt{Bayescan}$ analysis, here
we used all the individuals. For each species, for each type of genetic
variation present, we used Gower distances (Gower 1971) to express the
genomic differences between individuals (using the cluster R package to
accommodate sparsity; Maechler \emph{et al.} 2015). These distances were
subject to a non metric multi-dimensional scaling analysis (implemented
in the vegan R package using K=2 and 2 random starts; Table S3; Oksanen
\emph{et al.} 2015). The average of the ordinated values associated with
individuals in each grid cell we used to characterize the genomic
variation in the grid cell.

\subsubsection{Prioritizations}\label{prioritizations}

We used the unreliable representative and adequate prioritization (URAP)
formulation of the reserve selection problem (Hanson \emph{et al.}
2016). We treated the genomic and surrogate variables as distinct
attribute spaces. We set the demand points for each species and its
attribute space using the values associated with the planning units.
First, we generated a set of single species prioritizations. For each
species, we generated a prioritization using a 20\% amount-based target,
a prioritization using a 20\% amount-based target and 90\% space-based
targets for the surrogate variation, and a prioritization using a 20\%
amount-based target and 90\% space-based targets for the genomic
variation. Next, we generated three multi-species prioritizations using
the same sets of targets used in the single species prioritizations.
Finally, to understand the relationship between the surrogate-based and
genomic-based targets, we generated a suite of prioritizations using
increasing space-based targets between 1\% and 100\% in increments of
49.5\%. For each prioritization we calculated the proportion of the
adaptive (if present) and neutral genetic variation that it secured. We
solved the reserve selection problems to within 90\% of optimality using
the $\texttt{rapr}$ R package (Hanson \emph{et al.} 2016) and
$\texttt{Gurobi}$ (Gurobi Optimization 2015).

\subsection{Results}\label{results}

\subsubsection{Single species
prioritizations}\label{single-species-prioritizations}

\subsubsection{Multi-species
prioritisations}\label{multi-species-prioritisations}

\subsubsection{Pareo-frontier analysis}\label{pareo-frontier-analysis}

\subsection{Discussion}\label{discussion}

\subsection{Acknowledgements}\label{acknowledgements}

JOH is funded by an Australian Postgraduate Award (APA) scholarship. RAF
has an Australian Research Council Future Fellowship. This work was
supported by the Centre of Excellence for Environmental Decisions (CEED)
and the Landscape Ecology and Conservation Group (LEC) at The University
of Queensland.

\subsection{References}\label{references}

Benjamini, Y., Hochberg, Y. (1995) Controlling the false discovery rate:
a practical and powerful approach to multiple testing. \emph{Journal of
the Royal Statistical Society. Series B (Methodological)}. \textbf{57},
289--300.

Bothwell, H., Bisbing, S., Therkildsen, N., Crawford, L., Alvarez, N.,
Holderegger, R., Manel, S. (2013) Identifying genetic signatures of
selection in a non-model species, alpine gentian (gentiana nivalis l.),
using a landscape genetic approach. \emph{Conservation Genetics}.
\textbf{14}, 467--481.

Evanno, G., Regnaut, S., Goudet, J. (2005) Detecting the number of
clusters of individuals using the software structure: a simulation
study. \emph{Molecular Ecology}. \textbf{14}, 2611--2620.

Falush, D., Stephens, M., Pritchard, J. K. (2007) Inference of
population structure using multilocus genotype data: dominant markers
and null alleles. \emph{Molecular Ecology Notes}. \textbf{7}, 574--578.

Foll, M., Gaggiotti, O. (2008) A genome-scan method to identify selected
loci appropriate for both dominant and codominant markers: A bayesian
perspective. \emph{Genetics}. \textbf{180}, 977--993.

Gower, J. C. (1971) A general coefficient of similarity and some of its
properties. \emph{Biometrics}. \textbf{27}, 857--871.

Gugerli, F., Englisch, T., Niklfeld, H., Tribsch, A., Mirek, Z.,
Ronikier, M., Zimmermann, N., Holderegger, R., Taberlet, P. (2008)
Relationships among levels of biodiversity and the relevance of
intraspecific diversity in conservation - a project synopsis.
\emph{Perspectives in Plant Ecology, Evolution and Systematics}.
\textbf{10}, 259--281.

Gurobi Optimization, I. (2015) Gurobi optimizer reference manual.

Hanson, J. O., Rhodes, J. R., Possingham, H. P., Fuller, R. A. (2016)
rapr: representative and adequate prioritisations in r.
\emph{Unpublished}. \textbf{X}, XX--XX.

Hijmans, R. J., Cameron, S. E., Parra, J. L., Jones, P. G., Jarvis, A.
(2005) Very high resolution interpolated climate surfaces for global
land areas. \emph{International Journal of Climatology}. \textbf{25},
1965--1978.

Jakobsson, M., Rosenberg, N. A. (2007) CLUMPP: a cluster matching and
permutation program for dealing with label switching and multimodality
in analysis of population structure. \emph{Bioinformatics}. \textbf{23},
1801--1806.

Maechler, M., Rousseeuw, P., Struyf, A., Hubert, M., Hornik, K. (2015)
\emph{cluster: Cluster analysis basics and extensions}.

Meirmans, P., Goudet, J., IntraBioDiv Consortium, Gaggiotti, O. (2011)
Ecology and life history affect different aspects of the population
structure of 27 high-alpine plants. \emph{Molecular Ecology}.
\textbf{20}, 3144--3155.

Oksanen, J., Blanchet, F. G., Kindt, R., Legendre, P., Minchin, P. R.,
O'Hara, R. B., Simpson, G. L., Solymos, P., Stevens, M. H. H., Wagner,
H. (2015) \emph{vegan: Community ecology package}.

P{é}rez-Figueroa, A., Garc{í}a-Pereira, M. J., Saura, M.,
Rol{á}n-{Á}lvarez, E., Caballero, A. (2010) Comparing three different
methods to detect selective loci using dominant markers. \emph{Journal
of Evolutionary Biology}. \textbf{23}, 2267--2276.

Pritchard, J. K., Stephens, M., Donnelly, P. (2000) Inference of
population structure using multilocus genotype data. \emph{Genetics}.
\textbf{155}, 945--959.

Vos, P., Hogers, R., Bleeker, M., Reijans, M., Lee, T. van de, Hornes,
M., Friters, A., Pot, J., Paleman, J., Kuiper, M., Zabeau, M. (1995)
AFLP: a new technique for dNA fingerprinting. \emph{Nucleic Acids
Research}. \textbf{23}, 4407--4414.

\includepdf[pages=-]{figures.pdf}
\includepdf[pages=-]{supporting_information.pdf}

\end{document}

>>>>

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% load packages
\usepackage{float}
\usepackage{listings}
\lstset{numbers=left}

% define struts for tables
\newcommand\T{\rule{0pt}{2.6ex}} %top strut
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % bottom strut

\templatetype{pnasresearcharticle}  % Choose template

\title{Environmental and geographic variables are effective surrogates for
genetic variation in conservation planning}

\author[a,1]{Jeffrey O. Hanson}
\author[b]{Jonathan R. Rhodes}
\author[a]{Cynthia Riginos}
\author[a]{Richard A. Fuller}

  \affil[a]{School of Biological Sciences, The University of Queensland, Brisbane,
QLD, Australia}
  \affil[b]{School of Earth and Environmental Sciences, The University of
Queensland, Brisbane, QLD, Australia}

% Please give the surname of the lead author for the running footer
\leadauthor{Hanson}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{To protect biodiversity for the long term, nature reserves and other
protected areas need to represent a broad range of different genetic
types. However, genetic data are expensive and time consuming to obtain.
Here we show that freely available environmental and geographic
variables can be used as effective surrogates for genetic data in
conservation planning. This means that conservation planners can, with
some confidence, design protected area systems to represent
intra-specific genetic diversity without investing in expensive
programmes to obtain and analyze genetic data.}

\authorcontributions{JOH performed the analyses. All authors developed the study and drafted
the manuscript.}

\authordeclaration{The authors declare no conflict of interest.}

\correspondingauthor{\textsuperscript{1} To whom correspondence should be addressed: E-mail: jeffrey.hanson@uqconnect.edu.au.}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 \keywords{  conservation |  biodiversity |  AFLP |  genetic diversity   }

\begin{abstract}
Protected areas buffer species from anthropogenic threats and provide
places for the processes that generate and maintain biodiversity to
continue. However, genetic variation, the raw material for evolution, is
difficult to capture in conservation planning, not least because genetic
data require considerable resources to obtain and analyze. Here we show
that freely available environmental and geographic distance variables
are highly effective surrogates in conservation planning for
representing adaptive and neutral intra-specific genetic variation. We
obtained occurrence and genetic data from the IntraBioDiv project for 27
alpine plant species collected over the European Alps using a gridded
sampling scheme. For each species, we identified loci that were
potentially under selection using outlier loci methods, and mapped their
main gradients of adaptive and neutral genetic variation across the grid
cells. We then used the cells as planning units to prioritize protected
area acquisitions. First, we verified that the spatial patterns of
environmental and geographic variation were correlated, respectively,
with adaptive and neutral genetic variation. Second, we showed that
these surrogates can predict the proportion of genetic variation secured
in randomly generated solutions. Finally, we discovered that solutions
based only on surrogate information secured substantial amounts of
adaptive and neutral genetic variation. Our work paves the way for
widespread integration of surrogates for genetic variation into
conservation planning.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

@@

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

\acknow{JOH is funded by an Australian Postgraduate Award (APA) scholarship. RAF
has an Australian Research Council Future Fellowship.}

\dropcap{P}rotected areas spearhead conservation efforts (1). They
buffer species from anthropogenic impacts, providing places for them to
persist. Since the resources available for conservation are limited,
protected areas need to be sited in places that fulfill conservation
objectives for minimal cost (2). To achieve this, conservation planning
exercises often generate plans for entire networks of protected areas
(prioritizations) to allocate resources cost-effectively and preserve
broad-scale biodiversity processes (3). Intra-specific genetic variation
is fundamental to long-term species persistence (4, 5), and as a
consequence, there has been increasing interest in designing
prioritizations that represent this aspect of biodiversity (6--10).

Although the strength of natural selection is a continuous force,
genetic variation is often classified as adaptive or neutral (reviewed
in 11). Adaptive genetic variation is associated with loci that
significantly affect fitness. Typically, such ``adaptive'' loci are
detected due to anomalous patterns among individuals (eg. 12, 13),
though phenotypic-genetic associations are more likely to identify
functionally important genomic regions for individual species (eg. 14).
By representing the full range of adaptive variation, protected areas
can help ensure that populations with particularly beneficial
adaptations are not lost (7, 15). In contrast, neutral genetic variation
is associated with loci that do not significantly affect fitness, but
instead reflect the evolutionary history of different populations. By
representing the full range of neutral variation, protected areas can
safeguard against the adverse effects of low genetic diversity (6). Thus
optimally sited protected area networks would aim to represent patterns
of both adaptive and neutral genetic variation (6, 7, 15).

Recently, the use of surrogate data has been proposed to generate
prioritizations that capture intra-specific genetic variation (16,
17)---without needing to utilize genetic data to achieve this. Since
adaptation is ultimately driven by selection pressures, environmental
variables have been proposed as surrogates for adaptive genetic
variation (eg. 16, 18). Specifically, by conserving individuals in a
broad range of environmental conditions, we might expect to capture
individuals with a diverse set of local adaptations, and overall capture
a large proportion of the adaptive genetic variation present in the
species. However, the effectiveness of this approach remains unverified.
Neutral genetic variation arises from a reduction in gene flow between
populations. Over the last few years, the field of phylogeography has
predominantly focused on describing neutral genetic diversity, and so
the landscape factors that affect neutral variation are relatively well
understood (reviewed in 19). Potential surrogates for neutral genetic
variation have been based on variables that predict the level of
connectivity between different areas. For instance, according the
isolation by distance model (IBD; 20), populations located further apart
are predicted experience less gene flow, and in turn, share fewer
neutral loci. Based on this idea, spreading conservation priorities
evenly across the geographic distribution of an island network has been
found to capture more neutral genetic variation (17). However this
remains untested in spatially contiguous systems where connectivity is
complicated by many additional factors (eg. land use; 21)---the typical
situation in most conservation planning exercises.

Here we determine whether environmental and geographic surrogates
capture adaptive and neutral genetic variation respectively in the
context of conservation planning. We use distribution and genomic data
for 27 alpine plant species in the European Alps that was obtained by
the IntraBioDiv project (22). The data was collected following a gridded
sampling scheme which we adopted as planning units for this study. We
show that for most species the spatial patterns of adaptive and neutral
genetic variation correlated with environmental and geographic
variables. We also show that for most species the level of association
is strong enough to be operational for conservation planning. Finally,
we demonstrate that using these surrogates results in prioritizations
that secure a substantial proportion of intra-specific genetic
variation.

\section*{Results}\label{results}
% \addcontentsline{toc}{section}{Results}

We detected putatively adaptive genetic variation in ten of the 27 plant
species. We used two outlier detection methods---that solely used
genetic data and did not use environmental data---to identify loci under
selection. These methods returned reasonably consistent results (mean
87.92 \% loci per species assigned the same classification \(\pm\) 8.75
SD; Table S1). Of the species that were associated with adaptive genetic
variation, only a small proportion of loci were classified as being
adaptive (mean 3.01 \% loci per species \(\pm\) 1.95 SD). After
identifying the loci showing strong signals of selection, we used
non-metric multi-dimensional scaling (NMDS) analyses to identify the
main gradients of adaptive (if detected) and neutral variation for each
species. Generally, only a small number of continuous dimensions was
needed to sufficiently describe their patterns of adaptive (\(K = 2\)
for all species; Table S2) and neutral genetic variation
(\(2 \leq K \leq 4\) for all species; Table S1). The resulting
ordinations were used to construct an adaptive (if detected) and neutral
genetic space for each species. The spatial distribution of these
genetic spaces (Figures S1--S27) generally showed substantial spatial
auto-correlation (eg. \emph{Cerastium uniflorum}, Figure S34;
\emph{Dryas octopetala}, Figure S36), suggesting that the environmental
and geographic variables have potential to be effective surrogates for
genetic variation.

We verified that the spatial patterns in environmental variation
correlated with the broad-scale patterns in adaptive genetic variation
for each species. We also verified that there was a correlation between
neutral genetic variation and variation in geographic position. For each
species, we constructed dissimilarity matrices expressing differences
between the planning units where individuals were detected based on the
units' (i) environmental characteristics, (ii) geographic position, and
also the (iii) adaptive (if adaptive loci detected), and (iv) neutral
genetic characteristics of the individuals found inside them. The
spatial patterns of environmental variation were significantly
correlated with the pattern of adaptive genetic variation for eight of
the ten species associated with adaptive variation (\emph{P} \textless{}
0.05; mean 0.09 marginal \(R^2\) \(\pm\) 0.06 SD for significant models;
Table S3). Similarly, geographic distance between planning units was
also correlated significantly with the spatial pattern of neutral
genetic variation among planning units for 26 of the 27 species
(\emph{P} \textless{} 0.05; mean 0.2 marginal \(R^2\) \(\pm\) 0.16 SD
for significant models; Table S3). Thus, for most species, planning
units that contained different environmental conditions contained
individuals with different adaptive genetic characteristics, and
planning units that were further apart tended to contain individuals
with different neutral genetic characteristics. After verifying these
patterns were correlated, our next step was to determine whether these
associations were strong enough to be effective for conservation
planning.

For each species, we generated a suite of 10,000 random prioritizations,
and calculated the proportion of environmental variation and adaptive
(if present) genetic variation that each prioritization captured. We
then repeated this process, and calculated the proportion of variation
in geographic position and neutral genetic variation they sampled. The
environmental and geographic variables were moderately effective
predictors for the genetic variation represented by the randomly
generated prioritizations (Figures 1, S28 and S29). The relationship
between the proportion of genetic and surrogate variation secured in the
prioritizations varied among the species (species \(\times\) proportion
of environmental variation interaction term:
\({\chi^2}_{9} = {6776.94}; P 0.028\); species \(\times\) proportion of
geographic variation interaction term:
\({\chi^2}_{26} = 4.670631\times 10^{4}\); \(P =\) \textless{} 0.001).
\emph{Post-hoc} analyses showed that these relationships were positive
for all species (environmental: minimum \textit{z} = 40.34, maximum
\(P < 0.001\); geographic: minimum \textit{z} = 23.51, maximum
\(P < 0.001\); Table S4). After establishing that the the proportion of
surrogate variation secured in a prioritization also predicted the
proportion of genetic variation it secured, our final step was to
determine if prioritizations were more effective when generated using
targets based on the surrogate variables.

\begin{figure}

{\centering \includegraphics[width=3.42in,height=2.5in]{article_files/figure-latex/unnamed-chunk-3-1.pdf}

}

\caption{The proportion of adaptive (a; 10 species) and neutral (b; 27 species) genetic variation represented in a suite of randomly generated prioritizations for different species as a function of the surrogate variation they also secured (lines). Panels (c) and (d) show the distribution of $R^2$ values for the 37 models shown in (a) and (b).}\label{fig:unnamed-chunk-3}
\end{figure}

To determine whether environmental and geographic targets could improve
the effectiveness of prioritizations in representing genetic variation,
we generated prioritizations using (i) ``amount targets'' reflecting the
traditional approach of representing a certain proportion of each
species' geographic distribution, (ii) ``amount and surrogate targets''
where we targeted representation of the environmental and geographic
surrogates as well as a certain proportion of each species' geographic
distribution, and (iii) ``amount and genetic targets'' where we targeted
representation of the directly measured genetic variation as well as a
certain proportion of each species' geographic distribution. To
determine if these patterns were robust, for each of the three
combinations of the targets, we generated prioritizations under four
scenarios: (i) single-species with equal costs, (ii) single species with
acquisition costs, (iii) multi-species with equal costs, and (iv)
multi-species with acquisition costs (Figure S30).

\begin{figure}

{\centering \includegraphics[width=3.42in,height=4in]{article_files/figure-latex/unnamed-chunk-4-1.pdf}

}

\caption{The proportion of adaptive and neutral genetic variation secured for each species in solutions based on different targets and scenarios. Box plots show the median, and the 25th and 75th percentiles. Whiskers show the data at 1.5 times the inter-quantile range. Points show data outside the whiskers. Red lines show the target proportion of genetic variation.}\label{fig:unnamed-chunk-4}
\end{figure}

The proportion of genetic variation secured in a prioritization depended
on the targets used to generate the prioritization
(\({\chi^2}_{2} = 67.81\); \(P < 0.001)\). Most notably, prioritizations
based on the surrogate variables represented significantly more genetic
variation than amount-based prioritizations (93.24 \% \(\pm\) 13.79 SD
overall genetic variation secured versus 78.33 \% \(\pm\) 23.62 SD;
\(Z_1 = 4.59\); \(P < 0.001\)), and were not distinguishable from
prioritizations based on measured genetic data (94.7 \% \(\pm\) 3.8 SD;
\(Z_1 = 0.56\); \(P > 0.99\)). These results indicate that environmental
and geographic surrogates in this case far outperform traditional
amount-based conservation planning, and perform almost as well as a
conservation plan based directly on measured genetic data.

Overall, the prioritizations tended to secure a greater proportion of
adaptive genetic variation than neutral genetic variation (adaptive:
mean 96.04 \% \(\pm\) 7.61 secured across all prioritizations, neutral:
mean 71.94 \(\pm\) 24.16; \({\chi^2}_{1} = 1408.16\); \emph{P}
\textless{} 0.001). Thus, regardless of the targets used to generate a
prioritization, or the planning context under which the prioritization
was generated, prioritizations tend to secure more adaptive than neutral
genetic genetic variation.

The average proportion of genetic variation secured by prioritizations
varied under different scenarios (\({\chi^2}_{3} = 34.45\); \emph{P}
\textless{} 0.001). Specifically, prioritizations generated under
single-species scenario (mean 78.36 \% genetic variation secured \(\pm\)
23.61) secured less genetic variation than those under the single
species with opportunity costs (mean 88.89 \% genetic variation secured
\(\pm\) 15.52; \(Z_1 = 2.94\); \(P = 0.02\)) or the multi-species with
cost scenarios (mean 91.89 \% genetic variation secured \(\pm\) 12.31;
\(Z_1 = 3.68\); \(P = 0.001\)). These results suggest the amount of
genetic variation secured in a prioritization may be affected by the
data used to represent acquisition cost.

\section*{Discussion}\label{discussion}
% \addcontentsline{toc}{section}{Discussion}

We have shown that broad-scale environmental and geographic variables
can be effective as surrogates for adaptive and neutral genetic
variation in conservation planning. Our study is the first to show this
using field measurements of genetic variation for a broad range of
species. The spatial patterns of environmental and geographic surrogates
were strongly correlated with the patterns of adaptive and neutral
genetic variation for most species. Moreover, for most species,
prioritizations generated using environmental and geographic targets
secured a greater proportion of adaptive and neutral genetic variation
than traditional conservation planning. These environmental and
geographic surrogates were based on freely available data, and could be
applied to any study region across the world.

Our results demonstrate that environmental and geographic variables are
effective surrogates for most species considered here (Figure 2).
Despite this, geographic distance was a suprisingly poor surrogate for
neutral genetic variation for a few species (eg. \emph{Gypsophila
repens}: \(R^2\) = 0.26; \emph{Luzula alpinopilosa}: \(R^2\) = 0.28;
\emph{Gentiana nivalis} \(R^2\) = 0.29). One explanation for this result
is that geographic distance will be a poor surrogate for neutral genetic
variation where spatial genetic structure is complicated by additional
factors (21, 23). For example, some species can maintain relatively high
connectivity between distant populations (eg. wind dispersing plants;
22), and in some places can be disrupted by landscape features (eg.
anthropogenically modified land 21). Overall, such species were the
exception in our analysis, and both surrogates performed moderately well
for most species.

Our results show that environmental and geographic surrogates can be
used to capture genetic variation in prioritizations, the next question
is: what percentage of surrogate variation should planners target to
preserve genetic variation? To secure at least 90 \% of the species'
neutral genetic variation, prioritizations needed to sample 95.07 \%
\(\pm\) 6.1 SD of the variation in geographic position among the
planning units occupied by each species. Additionally, to secure at
least 90 \% of each species' adaptive genetic variation, prioritizations
needed to sample 56.43 \% \(\pm\) 7.54 SD of the environmental variation
in planning units occupied each the species. For all species, however,
it was possible to generate solutions that secured a large proportion of
the surrogate variation (\textgreater{} 90 \%) and only a small
proportion of genetic variation (\textless{} 20 \%; Figures S56--S57).
Planners may avoid such outcomes by using both amount- and
surrogate-based targets. Depending on the study area and the species of
conservation interest, higher targets may be needed to increase the
likelihood that prioritizations will secure a large proportion of the
intra-specific genetic variation for all of the species in the planning
exercise.

Our results suggest that conservation planners can secure a reasonably
representative sample of the intra-specific adaptive genetic variation
using only amount-based targets (Figure 2). For most species, the
spatial patterns of adaptive genetic variation clustered into a few
distinct groups (eg. \emph{Carex sempervirens} and \emph{Cerastium
uniflorum}; Figures S33 and S34 respectively). As a consequence, a
prioritization would only need to select a single planning unit in each
cluster to secure a representative sample. This mechanism explains why
adaptive variation accumulated much more quickly than neutral genetic
variation in the randomly generated prioritizations. Additionally, this
mechanism also explains why the single-species prioritizations generated
using only amount targets were often able to achieve high
representation---they were essentially a random selection and so
frequently contained planning units in different parts of the species'
ranges (Figure 4a). Overall---and contrary to our original
hypothesis---it seems that conventional reserve selection methods might
often conserve species' adaptive genetic variation.

There are several limitations associated with our analysis. Firstly, the
size of the planning units we used (approx. 23 \(\times\) 25 km) is much
larger than typically used in regional conservation planning (1--10
km\(^2\)). We used this resolution because the genetic data were
collected at this scale. Whilst we could have interpolated the genetic
data to a finer resolution and used smaller planning units, this would
have biased our analysis by artificially introducing additional spatial
auto-correlation. Secondly, we used geographic distances as surrogates
for neutral genetic variation, yet distances that incorporate data on
topography may better describe connectivity in the study area. However,
such distances often require species-specific scaling (eg. 21), and so
cannot easily be utilized in multi-species planning exercises. Thirdly,
we used amplified fragment length polymorphism data (AFLP; 24) to
describe genetic variation. Whilst next-generation sequencing provides
higher resolution genetic information than AFLP data (11), we know of no
suitable multi-species genomic data set, and our methodology would still
have utilized only the main gradients of the genetic variation to
generate prioritizations in a feasible period of time. Furthermore, even
with modern population genomic approaches, a survey can at best hope to
identify markers that are linked to functionally adaptive variants.

Broad-scale environmental and geographic variables are generally
effective surrogates for representing adaptive and neutral genetic
variation for most species in our study system. Moreover, data to
calculate the surrogate variables are freely available for any location
in the world. Careful use of such surrogates in conservation planning
could vastly improve the chances of long-term biodiversity persistence
for relatively little additional cost.

\section*{Materials and Methods}\label{materials-and-methods}
% \addcontentsline{toc}{section}{Materials and Methods}

\subsection*{Study system}\label{study-system}
% \addcontentsline{toc}{subsection}{Study system}
